Fractional Types

### 2016-12-18 typespp.tex
Fix a typo

The last new syntactic category in $\Pi^/$ is that of values which deserves some
additional discussion. When types denote sets, values of a type are clear:
they are just the elements of the set.  In the case when types are groupoids,
this is less clear, especially when the groupoid cardinality is a proper
fraction.  What we get instead are equivalence classes of values.
The idea is not uncommon: in the conventional $\lambda$-calculus, we list
$\lambda x.x$ and $\lambda y.y$ as separate values of type
$\tau \rightarrow \tau$ and then provide a separate equivalence relation
($\alpha$-equivalence) to express the fact that these two values are
indistinguishable. The treatment in our setting is similar: for iteration
groupoids $\order{c}$, every distinct iterate $c^k$ is a listed as a separate
value with the understanding that some iterates are
$\isotwo$-equivalent. Similarly for symmetry groupoids $\iorder{c}$, every
morphism is listed as a value $1/c^k$ with the same understanding that that some
of these morphisms are $\isotwo$-equivalent.

>>>>

The last new syntactic category in $\Pi^/$ is that of values which deserves some
additional discussion. When types denote sets, values of a type are clear: they
are just the elements of the set.  In the case when types are groupoids, this is
less clear, especially when the groupoid cardinality is a proper fraction.  What
we get instead are equivalence classes of values.  The idea is not uncommon: in
the conventional $\lambda$-calculus, we list $\lambda x.x$ and $\lambda y.y$ as
separate values of type $\tau \rightarrow \tau$ and then provide a separate
equivalence relation ($\alpha$-equivalence) to express the fact that these two
values are indistinguishable. The treatment in our setting is similar: for
iteration groupoids $\order{c}$, every distinct iterate $c^k$ is listed as a
separate value with the understanding that some iterates are
$\isotwo$-equivalent. Similarly for symmetry groupoids $\iorder{c}$, every
morphism is listed as a value $1/c^k$ with the same understanding that some of
these morphisms are $\isotwo$-equivalent.
